Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-08 paper/paper_new.tex
Updates from Overleaf

\section{Discussion}
Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, to improve and enrich metadata that enables researchers to perform advanced specimen image analysis and investigate scientific research questions on a scale that has never been pursued before. Our investigation has thus far focused on fish as the specimen of study. Fish are vertebrate animals (phylum Chordata), with over \(34,000\) known unique species~\cite{fishbase}, and likely many more undiscovered. Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype information. The ability to analyze thousands of images of a single fish species computationally can lead to new discoveries that are impossible to pursue manually. Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress~\cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity for useful metadata. Efforts to integrate such methods in digital libraries as a means of automatic metadata generation, particularly for digitized specimens, appear to still be somewhat limited. This is likely due to the diversity of image shapes, sizes and the inconsistent configurations of specimens, labels, rulers, etc.\ within them. Object detection as explored in our research, working with an established architecture, is applicable the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research. And following object detection, one can apply pixel analysis to computer many more higher order properties from the initial segmentation information.
%can we say something here.

>>>>

\section{Discussion}
Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, to improve and enrich metadata that enables researchers to perform advanced specimen image analysis and investigate scientific research questions on a scale that has never been pursued before. Our investigation has thus far focused on fish as the specimen of study. Fish are vertebrate animals (phylum Chordata), with over \(34,000\) known unique species~\cite{fishbase}, and likely many more undiscovered. Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype information. The ability to analyze thousands of images of a single fish species computationally can lead to new discoveries that are impossible to pursue manually. Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress~\cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity to automatically generate useful metadata. Efforts to integrate such automatic metadata generation methods into digital library workflows and architectures still seem limited.
%content based information retrieval (CBIR) for digital library images\cite{ivanova2011content}
%Link above is from the EU counterpart to JCDL, and trying to weave in, just focuses on color semantics, if we want to get another citation in there.
This is likely due to the diversity of image shapes, sizes and the inconsistent configurations of specimens, labels, rulers, etc.\ within them. Object detection as explored in our research, working with an established architecture, is applicable the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research. And following object detection, one can apply pixel analysis to computer many more higher order properties from the initial segmentation information.
%can we say something here.
